Targeted interrogation of mutational hotspots in rheumatoid arthritis

### 2024-03-12 scomatic/reports/targeted_mutation_calling.Rmd
create separated targeted_mutation_calling step, move dndscv run to pre-processing

---
title: "Targeted interrogation of mutational hotspots in rheumatoid arthritis"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: true
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
  cache_dir: './target_mutation_calling_cache/'
  rerun: true
---

@@

# recursites (to add detected mut)
recurmuts <-
  readr::read_tsv('recursites.tsv') %>%
  dplyr::transmute(
    chr,
    mut_pos = pos,
    mut_pos_lab = paste0(pos, '\ mut: ', mut)
  )

@@

>>>>

---
title: "Targeted interrogation of mutational hotspots in rheumatoid arthritis"
author: "Alexandra Tidd"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    fig_width: 8
    keep_md: true
    code_folding: show
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 4
    theme: lumen
params:
  recursites: NULL
  cache_dir: './target_mutation_calling_cache/'
  rerun: true
---

@@

# recursites (to add detected mut)
recursites <-
  readr::read_tsv(params$recursites) 
recurmuts <-
  recursites %>%
  dplyr::transmute(
    chr,
    mut_pos = pos,
    mut_pos_lab = paste0(pos, '\ mut: ', mut)
  )

@@

## Recurrent mutations sites

Recurrent mutations from the LCM-WES data were found using `dNdScv`. Mutated sites in the following genes will be interrogated.

```{r plot_recurmuts, fig.width = 10, eval = F}
recursites %>%
  dplyr::group_by(gene) %>%
  dplyr::mutate(sum_freq = sum(freq)) %>%
  ggplot(aes(x = reorder(gene, -sum_freq), y = freq, fill = qval)) +
  geom_col(position = 'stack') +
  scale_x_discrete(guide = guide_axis(angle = -90)) +
  labs(x = 'gene') +
  theme_classic()
```
